%%%%
% MTecknology's Resume
%%%%
% Author: Michael Lustfield
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
	{\Huge\color{accentTitle} #1}
	\vspace{10pt}
	{\color{accentLine} \hrule}
	\vspace{2pt}
	%{\footnotesize\color{accentTitle} #2}
	\footnotesize{#2}
	\vspace{2pt}
	{\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% John Doe's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{Jianda Chien}{
	% Web Version
	%\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
	%\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
	%%
	\href{tel:+886 919138697}{
	  \raisebox{-0.05\height} \faPhone\ +886 919138697} ~ | ~
	\href{mailto:jianda851013@gmail.com}{
	  \raisebox{-0.15\height} \faEnvelope\ jianda851013@gmail.com} ~ | ~
	\href{https://www.linkedin.com/in/tsung-you-chien-66ba471bb/}{
	  \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/tsung-you-chien}
  }

  %--------%
  % Skills %
  %--------%

  \section{Skills}

  \begin{multicols}{2}
	\begin{itemize}[itemsep=2px, parsep=1pt, leftmargin=75pt]
	  \item[\textbf{Automation}] CloudFormation, AWS CDK, Gitlab CI
	  \item[\textbf{Container}] Docker, Podman, Kubernetes, Gitlab Container Registry
	  \item[\textbf{Languages}] Python, Node.js, Typescript, Bash
	  \item[\textbf{Policies}] NIST, HIPAA, FDA cybersecurity guideline
	  \item[\textbf{Tools}] CloudWatch, CloudTrail, Snyk, SonarQube, Sentry
	  \item[\textbf{Others}] Route53, VPC, Lambda, DynamoDB, S3
	\end{itemize}
  \end{multicols}

  %------------%
  % Experience %
  %------------%

  \section{Experience}

  \headingBf{PranaQ}{Nov 2022 -- Present}
  \headingIt{Software Engineer}{}
  \begin{resume_list}
	\vspace{6pt}
	\itemTitle{Operations}
	\item Architected and implemented CloudWatch monitoring dashboards, reducing incident response time by 75\%
	\item Designed and deployed multi-account AWS infrastructure using CloudFormation, managing dev, staging and production environments
	\item Established comprehensive CI/CD pipelines handling routine deployments
	\item Implemented security controls and compliance measures to achieve FDA cybersecurity guideline.
	\vspace{6pt}
	\itemTitle{Development}
	\item Architected and developed full-stack web application using TypeScript, Node.js, and React.
	\item Designed and implemented serverless architecture using AWS Lambda and API Gateway, and other AWS services such as DynamoDB, S3, SNS, SQS, etc.
	\item Optimized API latency, including reducing Lambda cold start time, DynamoDb Secondary Index configuration, and regional optimization.
	\item Implemented comprehensive error tracking and monitoring, achieving 95\% application reliability
	\vspace{6pt}
	\itemTitle{Others}
	\item Designed and executed zero-downtime DynamoDB migration strategy, successfully migrating 100+ GB of data while maintaining data integrity
	\item Implemented automated disaster recovery system with 2-hour RPO and 30-minute RTO objectives
	\item Architected multi-region DNS failover setup using Route53 for high availability
	\item Designed secure network architecture with isolated VPC subnets, implementing security groups and NACLs for enhanced protection
  \end{resume_list}

  \headingBf{Brilltek}{Mar 2020 -- Oct 2021}
  \headingIt{Backend Engineer}{}
  \begin{resume_list}
	\item Developed backend service with Node.js, and MariaDB.
	\item Build Docker images for projects and deployed to DockerHub.
	\item Refactor old projects to modern ES6 standards. Clean up code and improve code quality.
  \end{resume_list}

  %-----------%
  % Education %
  %-----------%

  \section{Education}

  \headingBf{National Chengchi University}{Sep 2021 -- Jan 2024} % Note: Adding year(s) exposes an implied age
  \headingIt{Master in Computer Science}{}
  \headingIt{Minors: Applied Cryptography}{}

  \headingBf{National Taiwan University}{Sep 2015 -- Jun 2019} % Note: Adding year(s) exposes an implied age
  \headingIt{Bachelor in Computer Science and Information Engineering}{}

  %----------------------------%
  % Extracurricular Activities %
  %----------------------------%

  \section{Activities}

  \headingBf{AWS Summit}{Jul 2024}
  \begin{resume_list}
	\item Speaker of AWS Summit Taipei Meetup sharing experience of using Control Tower and AWS Organizations.
	\item Sharing knowledge of AWS security and compliance to meet FDA compliance.
  \end{resume_list}

  \headingBf{Cryptography Algorithms Implementation}{2023}
  \begin{resume_list}
	\item Applied pbc and gmp library to implement cryptographic algorithms.
	\item Build Docker images for easy setup clean environment for development algorithms and testing.
  \end{resume_list}


\end{document}